### 2019-02-03 thesis_report/introduction.tex
updated intro

	Considering equation \eqref{eq:intro_ferm2maj} we can also write the Hamiltonian above using Majorana operators.
	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
	In figure, we discern two extremes:
	one is the situation where the pairing energy is minimal for Majorana pairs on the same site, the other is when the energy is minimal for pairing between of Majoranas from adjacent sites.

	Borrowing the analogy from the online course Topology in Condensed Matter\cite{noauthor_topology_2015}, we can see an electron as a domino stone: the two ends, seperated by a line, each correspond to a Majorona particle.
	In the figure below\cite{noauthor_topology_2015}, the dominoes, and thus electrons, have been placed in a chain:\\

	\begin{centering}
	\includegraphics[width=0.95\columnwidth]{images/majorana_dominoes}
	\end{centering}

	Corresponding to the system above, we have a Hamiltonian describing the physics of the system.

	In a regular system, the Majoranas on each end of stone are paired locally, as depicted in the figure below:\\

	\begin{centering}
	\includegraphics[width=0.95\columnwidth]{images/trivial_dominoes}
	\end{centering}

	Now suppose one would be able to shift the pairing, such that the Majoranas form pairs with the Majoranas on adjacent stones:\\

	\begin{centering}
	\includegraphics[width=0.95\columnwidth]{images/topological_dominoes}
	\end{centering}

	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
	This is the state we are interested in: the Majorana state, where two Majoranas are seperated in space.
	This physical seperation has the effect of not allowing simple local perturbations to disturb the system.

>>>>

	Considering equation \eqref{eq:intro_ferm2maj} we can also write the Hamiltonian above using Majorana operators.
	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
	In figure, we discern two extremes, one is the situation where the pairing energy is minimal for Majorana pairs on the same site:
	\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.95\columnwidth]{images/majorana_trivial_pairing}
	\caption{Trivial Majorana pairing in a Kitaev chain}
	\label{fig:trivial_majoranas}
	\end{figure}

	The other is when the energy is minimal for pairing between of Majoranas from adjacent sites:
	\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.95\columnwidth]{images/majorana_topological_pairing}
	\caption{Topological Majorana pairing in a Kitaev chain}
	\label{fig:topological_majoranas}
	\end{figure}

	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
	This is the state we are interested in: the Majorana state, where two Majoranas are seperated in space.
	This physical seperation has the effect of not allowing simple local perturbations to disturb the system, thus inherently protecting the system against decoherence.
